Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-06-13 paper/ms.tex
Elena edits
Update ms.tex
Adds some final touches for journal submission.

%\documentstyle[amssymb,12pt,draft,epsf,palatino]{nature-pvd}
\documentclass{natureprintstyle}
\bibliographystyle{naturemag}

@@

\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
% \usepackage{amssymb}
\usepackage{rotating,xcolor}
\usepackage{hyperref}
% \usepackage{tgbonum}
\usepackage[symbol]{footmisc}
\usepackage{placeins}

\usepackage{amsmath}

@@

@@

\item[Author Contributions] Foo.

  \item[Data Availability] Foo.

  \item[Code Availability] A public version of the AREPO code is available at
  \url{https://arepo-code.org/}.

>>>>

%\documentstyle[amssymb,12pt,draft,epsf,palatino]{nature-pvd}
\documentclass[twoside]{natureprintstyle}
\bibliographystyle{naturemag}

@@

\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
% \usepackage{amssymb}
\usepackage{rotating,xcolor}
\usepackage{hyperref}
% \usepackage{tgbonum}
\usepackage[symbol]{footmisc}
\usepackage{placeins}
\usepackage{amsmath}

% Adds line numbers, just for submission stage.
\usepackage[switch]{lineno}
\linenumbers

% Defines footer format for the date.
\usepackage{datetime}

\newdateformat{footerfmt}{%
\THEDAY\,\,\monthname[\THEMONTH]\,\,\THEYEAR}

% Adds current date to the footer.
\usepackage{fancyhdr}
% \fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[RO]{\textsc{\footerfmt\today}}
\fancyfoot[LE]{\textsc{\footerfmt\today}}
\pagestyle{fancy}

@@

% Enforces same format on first page as on subsequent pages.
\makeatletter
\let\ps@plain\ps@fancy
\makeatother

@@

\item[Author Contributions] A.B., L.H., and E.D. contributed to the conception
of the study. A.B. performed the simulations, led the analysis, and wrote the
manuscript. F.M. led and, J.Q., L.V.S., P.T., and M.V. contributed to the
development of the SMUGGLE code. All authors contributed to aspects of the
analysis.

\item[Data Availability]  Simulation output and initial conditions will be
made publicly available.

\item[Code Availability] A public version of the AREPO code is available at
\url{https://arepo-code.org/}. An associated GitHub repository containing
analysis and plotting scripts will be made publicly available (currently
private). For the submission stage, we have included a tarball of this
repository.
